\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-13 manuscript.tex
* IRT Finalize

We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always). As our purpose was to capture light exposure related behavior, ``Does not apply/I don't know'' and ``Never'' were providing similar information. As such we decided to collapse ``Does not apply/I don't know'' and ``Never'' options into one making it a 5 point Likert type response scale. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix (C. Desjardins \& Bulut, 2018) for the EFA. We employed principal axis (PA) as a factor extraction method with varimax rotation. PA is robust to the normality assumption violations (Watkins, 2020). The obtained latent structure was confirmed by another factor extraction method: the minimum residuals extraction method as well. We used a combination factor identification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018) We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.

@@

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) . The overall KMO vale for 48 items was 0.63 which was above the cutoff value (.50) indicating a mediocre sample (Hutcheson, 1999). Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions (Marida's test;(Mardia, 1970)). Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (C. Desjardins \& Bulut, 2018). Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA. However only 4.96\% of the inter-item correlation coefficients were greater than .30. The inter item correlation ranged between .44 to .91. And the corrected item-total correlations ranged between .10 to .44.

@@

\begin{longtable}{ccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:tabDes}Descriptive Statistics}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:tabDes} continued}}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endhead
Item1 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & .19\\
Item3 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
Item4 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
Item5 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
Item6 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
Item7 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
Item8 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
Item9 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & .28\\
Item11 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
Item12 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
Item13 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
Item14 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & .14\\
Item16 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
Item17 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
Item18 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
Item19 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
Item20 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
Item21 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
Item22 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
Item23 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
Item24 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
Item25 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
Item26 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
Item27 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
Item28 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
Item29 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
Item30 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
Item31 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
Item32 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
Item33 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
Item34 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
Item35 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
Item36 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
Item37 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
Item38 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
Item39 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
Item40 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
Item41 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
Item42 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
Item43 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
Item44 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
Item45 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
Item46 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
Item47 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
Item48 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

With initial 48 items we conducted three rounds of EFA gradually discarded problematic items. (cross-loading items and poor factor loading (\textless.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (Table\ref{tab:MinResTab}). Table\ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients. The commonalities ranged between .11 to .99. However, the histogram of the absolute values of non-redundant residual-correlations Fig\ref{fig:EFAResiduals} showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring. (C. D. Desjardins, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\ref{tab:sixFacTab}).

@@

We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(C. Desjardins \& Bulut, 2018). Several indices are suggested to measure model fit. These indices can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015). Absolute fit assess the model fit at an absolute level using indices including \(\chi^2\) test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model. Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero. Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices. Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of \(\chi^2\) test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit. Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model. Our fitted model failed to attain an absolute fit estimated by the \(\chi^2\) test. However, the \(\chi^2\) test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015). Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.-Y. Yu, 2002). Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA. Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = .12). Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).

@@

Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions (Kline, 2015; Putnick \& Bornstein, 2016). We used structural equation modeling framework to assess measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}. Our measurement invariance testing involved establishing configural, metric , scalar , and residual invariance (Widaman \& Reise, 1997). MI models are nested type models of which configural model is the first and least restrictive model. Configural model assumes that the number of factors and item number under each factors will be equal across two groups. Metric invariance model along with the assumption of configural model assumes that factor-loadings of the items across the two groups will be equal indicating each item contributes to the measured construct equivalently for the both groups. Along with these assumptions scalar invariance assumes that item intercepts to be equivalent across groups. Scalar invariance model indicates the equivalence of response scale across the groups, i.e.~persons with the same level of the underlying construct will score the same across the groups. Residual invariance model holds all the mentioned assumptions as true and also adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs. The invariance model fit was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above) , RMSEA (close to .06 or below). following the guidelines of Hu and Bentle (1999). We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.-Y. Yu, 2002). Table \ref{tab:InvarianceTab} summarized the fit indices. The comparison among different measurement invariance model was made by using \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attains the highest level of the MI. If the \(\Delta \chi^2\) is not statistically significant (p\textless0.05) (Dimitrov, 2010) the particular invariance model was accepted. We started our analysis by comparing the model fit of the lest restrictive model:configural model to metric MI model and continued successive comparisons. Table \ref{tab:InvarianceTab} indicates that our fiited model attains residual invariance: the highest level of invariance in terms of CFI, TLI, RMSEA and non-significant \(\Delta \chi^2\) test.

@@

\hypertarget{analysing-the-quality-of-items-by-item-information-theory}{%
\subsection{Analysing the quality of items by Item Information Theory}\label{analysing-the-quality-of-items-by-item-information-theory}}

We sought the IRT to gether information regarding the item quality. IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty(Baker, 2017). Here, an item's quality is judged based on item information in relation to participants' latent trait level (\(\theta\)). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\ref{tab:IRTparameters} to the combined EFA sample and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \textless.2) to develop the short form of LEBA. Baker (2017) categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \textgreater1.70. Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait. Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, \& 41) had relatively flat information curves thus discarded. We also gathered evidence of item fit and person fit to our fitted model.

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light}\label{fig:itmeinfo}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light}\label{fig:Testinfo}
\end{figure}

Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum. As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs. These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))). Also the amount of information changed rather steadily with the change of (\(\theta\)). Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor. The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.

Our result also indicated all the items fitted well to the respective models as assessed by assessed by RMSEA value obtained from Signed-X2 index implementation. All of the items had RMSEA value \textless.06 indicating adequate fit. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (C. Desjardins \& Bulut, 2018). We estimated the person fit statistics using standardized fit index Zh statistics (Drasgow, Levine, \& Williams, 1985). Zh \textless{} -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.

>>>>

For our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always). Our purpose was to capture light exposure related behavior and these two response options: ``Does not apply/I don't know'' and ``Never'' were providing similar information. As such we decided to collapse them into one making it a 5 point Likert type response scale. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used polychoric correlation matrix (Desjardins \& Bulut, 2018) for the EFA. We employed principal axis (PA) as factor extraction method with varimax rotation. PA is robust to the normality assumption violations (Watkins, 2020). The obtained latent structure was confirmed by another factor extraction method: ``the minimum residuals extraction'' as well. We used a combination of factor identification method including scree plot (Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method (Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018).
We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.

@@

\hypertarget{item-analysis}{%
\subsection{Item Analysis}\label{item-analysis}}

Table \ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items. Some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions {[}Marida's test;(Mardia, 1970){]}. Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (Desjardins \& Bulut, 2018). The corrected item-total correlation ranges between .03 -.48. No item was discarded based on descriptive statistics or item analysis.

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy (Kaiser, 1974) . The overall KMO vale for 48 items was 0.63 which was above the cutoff value (.50) indicating a mediocre sample (Hutcheson, 1999). Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA. However only 4.96\% of the inter-item correlation coefficients were greater than .30. The inter item correlation ranged between .44 to .91. And the corrected item-total correlations ranged between .03 to .48.

@@

\begin{longtable}{ccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:tabDes}Descriptive Statistics}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:tabDes} continued}}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endhead
Item1 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & 0.19\\
Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & 0.28\\
Item3 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & 0.23\\
Item4 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & 0.24\\
Item5 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & 0.17\\
Item6 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & 0.13\\
Item7 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & 0.32\\
Item8 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & 0.25\\
Item9 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & 0.08\\
Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & 0.42\\
Item11 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & 0.41\\
Item12 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & 0.48\\
Item13 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & 0.25\\
Item14 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & 0.28\\
Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & 0.03\\
Item16 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & 0.28\\
Item17 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & 0.21\\
Item18 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & 0.18\\
Item19 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & 0.17\\
Item20 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & 0.16\\
Item21 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & 0.21\\
Item22 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & 0.20\\
Item23 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & 0.08\\
Item24 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & 0.22\\
Item25 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & 0.15\\
Item26 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & 0.08\\
Item27 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & 0.17\\
Item28 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & 0.18\\
Item29 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & 0.13\\
Item30 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & 0.13\\
Item31 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & 0.39\\
Item32 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & 0.33\\
Item33 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & 0.37\\
Item34 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & 0.20\\
Item35 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & 0.20\\
Item36 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & 0.35\\
Item37 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & 0.09\\
Item38 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & 0.32\\
Item39 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & 0.07\\
Item40 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & 0.25\\
Item41 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & 0.14\\
Item42 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & 0.15\\
Item43 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & 0.22\\
Item44 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & 0.40\\
Item45 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & 0.29\\
Item46 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & 0.39\\
Item47 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & 0.37\\
Item48 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & 0.36\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (\textless.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (Table\ref{tab:MinResTab}). Table\ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients. The commonalities ranged between .11 to .99. However, the histogram of the absolute values of non-redundant residual-correlations Fig\ref{fig:EFAResiduals} showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring. (Desjardins \& Bulut, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\ref{tab:sixFacTab}).

@@

We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(Desjardins \& Bulut, 2018). Several indices are suggested to measure model fit. These indices can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015). Absolute fit assess the model fit at an absolute level using indices including \(\chi^2\) test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model. Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero. Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices. Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of \(\chi^2\) test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit. Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model. Our fitted model failed to attain an absolute fit estimated by the \(\chi^2\) test. However, the \(\chi^2\) test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015). Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.-Y. Yu, 2002). Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA. Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = .12). Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).

@@

Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions (Kline, 2015; Putnick \& Bornstein, 2016). We used a structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}. Our measurement invariance testing involved establishing configural, metric, scalar, and residual invariance (Widaman \& Reise, 1997). MI models are nested type models of which configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model, along with the assumption of the configural model, assumes that factor-loadings of the items across the two groups will be equal, indicating each item contributes to the measured construct equivalently for both groups. Along with these assumptions, scalar invariance assumes that item intercepts to be equivalent across groups. The scalar invariance model indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model holds all the mentioned assumptions as true and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs. The invariance model fit was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) (Hu \& Bentle, 1999). We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.-Y. Yu, 2002). Table \ref{tab:InvarianceTab} summarized the fit indices. The comparison among different measurement invariance models was made using the \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attains the highest level of the MI. If the \(\Delta \chi^2\) test for model fit is not statistically significant (p\textless0.05) (Dimitrov, 2010), the particular invariance model was accepted. We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons. Table \ref{tab:InvarianceTab} indicates that our fitted model had acceptable fit indices for all of the fitted MI models. The model fit does not significantly decrease across the nested models up to the scalar MI model. The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.

@@

\hypertarget{developing-short-form-of-leba}{%
\subsection{Developing Short form of LEBA}\label{developing-short-form-of-leba}}

We sought the item response theory (IRT) to develop the short form of LEBA. IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information(Baker, 2017). IRT judges the item's quality on item information in relation to participants' latent trait level (\(\theta\)). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (Samejima, Liden, \& Hambleton, 1997) to the combined EFA and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level (\(\theta\)), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \textless.2) to develop the short form of LEBA. Baker (2017) categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \textgreater1.70. Table \ref{tab:IRTparameters} summarizes the IRT parameters of our scale. Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level (\(\theta\)). Examination of the item information curve \ref{fig:itmeinfo} indicated 6 items (1, 25, 9, 38, 30, \& 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:itmeinfo}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Blue filter (b) Natural light (c) Smart device (d) Sleep environment (E) Electic light}\label{fig:Testinfo}
\end{figure}

Test information curve (TIC) (\ref{fig:Testinfo}) indicate the amount of information an the full-scale carry along the latent trait continuum. As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (\ref{fig:Testinfo}). These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))). Also the amount of information changed rather steadily with the change of (\(\theta\)). Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor. The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.

Table \ref{tab:itemfittab} summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by RMSEA value obtained from Signed-\(\chi^2\) index implementation. All of the items had RMSEA value \textless.06 indicating adequate fit. Figure \ref{fig:persornfit} depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (Desjardins \& Bulut, 2018). We estimated the person fit statistics using standardized fit index Zh statistics (Drasgow, Levine, \& Williams, 1985). Zh \textless{} -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.

\caption{\label{tab:itemfittab}}
